GPU Acceleration of the Material Point Method

### 2019-02-12 pres/pres.tex
red., scan

\end{minipage}
\end{frame}
\begin{frame}
Nvidia Nsight\cite{NVIDIA:METRICS} now offers metrics to identify bottlenecks:
\vspace{-5}
\begin{table}
  \footnotesize
  \begin{tabular}{ | l | l |}    \hline
    \textbf{Metric}   & \textbf{Description} \\ \hline
    VRAM SOL\%        & memory througput w.r.t. to hardware limit\\\hline
    SM SOL\%          & instruction throughput\\\hline
    L2 SOL\%          & L2-cache throughput\\\hline
    Tex SOL\%         & L1-cache throughput\\\hline
    SM Issue Util.\%  & amount of cycles an instr. was issued\\\hline
  \end{tabular}
\end{table}
\\
\vspace{5}
A simple map or copy shader with one instruction shows SoA vs. AoS differences:
\vspace{-15}
\begin{table}
  \footnotesize
  \begin{tabular}{ | l | l | l | l | l | l | l |}    \hline
    Layout &  $\Delta t_c (\mu s)$	& Speedup &VRAM     & SM     & L2     & SM Issue Util. \\\hline
    AoS         & 243                   & -       &77.7\%   & 7.3\%  & 30.3\% & 6.8\% \\\hline
    SoA         & \textbf{120}                   & 2.26x   &75.4\%   & \textbf{14.3}\% & 29.4\% & \textbf{14.0\%} \\
    \hline
\end{tabular}
\end{table}
$\Rightarrow$ SoA increases coalescing for non-random access.
\end{frame}
\subsection{Parallel Reduction \& Scan}
\begin{frame}
  \frametitle{Parallel Reduction \& Scan}
\end{frame}
\section{Delving Deeper: Further Opportunities}

>>>>

\end{minipage}
\end{frame}
\begin{frame}
Nvidia Nsight\cite{NVIDIA:METRICS} now offers metrics to identify bottlenecks:
\vspace{-5}
\begin{table}
  \footnotesize
  \begin{tabular}{ | l | l |}    \hline
    \textbf{Metric}   & \textbf{Description} \\ \hline
    VRAM SOL\%        & memory througput w.r.t. to hardware limit\\\hline
    SM SOL\%          & instruction throughput\\\hline
    L2 SOL\%          & L2-cache throughput\\\hline
    Tex SOL\%         & L1-cache throughput\\\hline
    SM Issue Util.\%  & amount of cycles an instr. was issued\\\hline
  \end{tabular}
\end{table}
\\
\vspace{5}
A simple map(\texttt{y=length(x)}) shader on 1024$\times$1024 Elements SoA vs. AoS differences:
\vspace{-15}
\begin{table}
  \footnotesize
  \begin{tabular}{ | l | l | l | l | l | l | l |}    \hline
    Layout &  $\Delta t_c (\mu s)$	& Speedup &VRAM     & SM     & L2     & SM Issue Util. \\\hline
    AoS(1 instr.)         & 243                   & -       &77.7\%   & 7.3\%  & 30.3\% & 6.8\% \\\hline
    SoA(1 instr.)         & \textbf{120}                   & 2.26x   &75.4\%   & \textbf{14.3}\% & 29.4\% & \textbf{14.0\%} \\\hline
    AoS(2 instr.)         & 275                   & -        &61.3\%           & \textbf{41.8}\% & \textbf{53.8}\% & 48.9\% \\\hline
    SoA(2 instr.)         & 240                   & 1.16x    &75.4\%  & 29.4\%          & 20.0\% & 62.3\% \\
    \hline
\end{tabular}
\end{table}
$\Rightarrow$ SoA increases coalescing for non-random access.
\end{frame}
\subsection{Parallel Reduction \& Scan}
\begin{frame}
\frametitle{Parallel Reduction \& Scan}
Assuming an associative \texttt{binary\_op(x,y)}:= $x \circ y$ , a neutral element $e$ of the \texttt{binary\_op}, and an array of values $\left[a_0,a_1, ... ,a_n\right]$.\\\vspace{10}
\begin{itemize}
  \item \textbf{Parallel reduction} computes the scalar:
\begin{equation}
  r = a_0 \circ a_1 \circ ... \circ a_n.
\end{equation}
\item (Exclusive) \textbf{scan} computes the array:
\begin{equation}
  \left[e , a_0 , \left(a_0 \circ a_1\right), \left(a_0 \circ a_1 \circ a_2\right), \ ... \ ,\left(a_0\circ a_1 \circ a_2 \circ ...\circ a_{n-1}\right)\right].
\end{equation}
\end{itemize}
\\\vspace{5}
Here, only shared memory approaches without (NVIDIA exclusive) warp shuffle operations.
\end{frame}
\begin{frame}
\textbf{Shared Memory Bank Conflicts}:
\\\vspace{5}
\begin{minipage}{0.94\textwidth}
\begin{minipage}{0.5\textwidth}
  \tiny
  \includesvg[svgpath =../images/,width=1.0\textwidth]{sequential}
  Sequential Addressing
\end{minipage}
\begin{minipage}{0.5\textwidth}
  \tiny
  \includesvg[svgpath =../images/,width=1.0\textwidth]{interleaved}
  Interleaved Addressing
\end{minipage}
\end{minipage}
\\\vspace{10}
Interleaved Addressing causes bank conflicts $\Rightarrow$ padding needed.
\textbf{Sequential work}:
\end{frame}
\section{Delving Deeper: Further Opportunities}
